Local Normalisation using the Empirical Null for Inspection of Additive Manufacturing using X-Rays

### 2019-04-09 reports/paper1/paper.tex
Initial paper commit

The aim of this project was to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.

Disagreement between the scan and \texttt{aRTist} can be found by subtracting one image from the other, any values too big in magnitude can be considered as a defect. However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus the comparisons should be done under the face of uncertainty.

A pixel by pixel inference was proposed to do defect detection. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan. Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal. Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the test statistics, assuming there are no defects, can be approximately quantified as
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, upper case $Z$ denote a random variable. Lower case $z$ denote a realisation or an observation of that random variable.

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$, can be calibrated, or trained, by holding out a number replicated x-ray images of a 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data and was used to train the variance model, such as a gamma distributed GLM. The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model. The variance was then predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable.

This method for inference was applied to the dataset \texttt{Sep16 120deg}. A cuboid (4 cm $\times$ 4 cm $\times$ 6 cm) with voids was purposefully manufactured to see if they can be detected, the CAD shown in Figure \ref{fig:inference_testObject}. The voids were of various diameters 2.4 mm, 1.2 mm, 0.6 mm and 0.3 mm. 6 voids for each diameter were designed in the CAD. Voids with diameters 2.4 mm and 0.6 mm were regularly arranged, otherwise they were arranged irregularly. The precision of the manufacturing was in the order of $\pm0.1\text{ mm}$.

@@

The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there. The test image and the \texttt{aRTist} simulation is shown in Figures \ref{fig:inference_inferenceIntro_inference_scan} and \ref{fig:inference_inferenceIntro_inference_artist} respectively.

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{X-ray image}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\texttt{aRTist} simulation}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{An x-ray image of a 3D printed cuboid, from the \texttt{Sep16 120deg} dataset, was compared to the \texttt{aRTist} simulation to detect the purposefully manufactured voids. The $p$-values obtained were used for hypothesis testing, using the \cite{benjamini1995controlling} procedure, at the 5\% FDR level. Pixels detected as positive are shown in red in d).}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

For each pixel, a test statistic was calculated. A test statistic too large in magnitude will classify that pixel as a positive result. In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be used to represent test statistic in a different way
\begin{equation}
  p_{x,y} = 2(1-\Phi(|z_{x,y}|))
\end{equation}
which can takes values $0\leqslant p_{x,y} \leqslant 1$. A $p$-value too small is considered a positive result. The $p$-values are shown in Figure \ref{fig:inference_inferenceIntro_inference_pvalue}.

The resulting $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Pixels are tested positive, or considered to be evidence of a defect, when $|z_{x,y}|>\inputNumber{../figures/inference/inferenceIntro_critical.txt}$. This value was chosen by controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} (BH) procedure. The positive pixels are shown in Figure \ref{fig:inference_inferenceIntro_inference_positivePixels}.

This proposed method for defect detection failed because too many false positives were detected. These false positives appear to have some structure, for example clustering in the corners or on surfaces. In addition, false negatives were detected because not all of the defects were detected.

Model misspecification appeared to be the main source of error. The test statistics and $p$-values were inspected in Figure \ref{fig:inference_inferenceIntro_histogram}. It can be seen that the majority of the test statistics does not look Normal. Also the majority of the $p$-values does not look uniformly distributed. This seems to suggest that the assumption of $Z_{x,y}\sim \normal(0,1)$ is incorrect.

\begin{figure}[htp]
  \centering
  \centerline{
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_histogram.eps}
    \caption{Histogram}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_pValue.eps}
    \caption{$p$-values}
    \label{fig:inference_inferenceIntro_pvalue}
  \end{subfigure}
}
  \caption{a) The histogram of the test statistics is compared with the standard Normal distribution. The standard Normal distribution is known as the null distribution in this scenario. b) The $p$-values are ordered and plotted. The critical region corresponds to controlling the false discovery rate at 5\% using the \cite{benjamini1995controlling} procedure. The dotted line shows the result if the $p$-values were uniformly distributed.}
  \label{fig:inference_inferenceIntro_histogram}
\end{figure}

This chapter recaps hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test. Assumptions used on the hypothesis testing can be relaxed by using the empirical null \citep{efron2004large}, which is reviewed here. The empirical null is then extended to an image filter, called the empirical null filter. This filter adjust each test statistic according to its neighbours, ironing out false positive results. Simulations and results are shown towards the end of the chapter.

\section{Literature Review}

Consider a test statistic from a pixel. If there are no defects, then the statistic is null and has the null distribution $Z|H_0\sim\normal(0,1)$. This can be described in another way by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis as $H_0:\mu=0$. A hypothesis test can judge how much $Z$ deviates from 0 by defining the alternative hypothesis $H_1:\mu\neq 0$. A statistic which does not have the null distribution is known as non-null.

In two-tailed hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical}, the $p$-value can be compared with the user defined significance level $\alpha$, also known as the size of the test in this specific example. A positive result is declared when $p<\alpha$, else it is a negative result. Correct and incorrect testing of the statistics can occur. For example testing a null statistic as positive is known as a false positive. It can be shown that $\alpha$ controls the false positive rate. $\alpha=5.0\%$ is a typical choice and was used throughout this thesis. Other fields use the $\sigma$ notation, for example $2\sigma$ correspond to about the $\alpha = 4.6\%$ significance level; this notation will not be used here.

Multiple hypothesis testing occurs when there are more than one hypotheses to test. For example $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \cdots, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\cdots,n$. The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\cdots,n$. Let the corresponding $p$-values be $p_1, p_2, \cdots, p_n$.

The uncorrected test classify any $p_i<\alpha$ as positive. This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}. This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}. PCER is the proportion of false positives out of all tests. The number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}. Using the notation, PCER is defined as
\begin{equation}
  \text{PCER}=
  \dfrac{1}{n}
  \expectation[V]
  \ .
\end{equation}
It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
\begin{equation}
  \text{PCER}\leqslant\alpha \ .
\end{equation}

\begin{table}[htp]
  \centering
  \begin{tabular}{c|c|c|c}
    &Negative&Positive&Total\\\hline
    Null & $U$ & $V$ & $n_0$\\
    Non-null & $T$ & $S$ & $n-n_0$\\\hline
    &$n-R$&$R$&$n$
  \end{tabular}
  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypothesis testing}
  \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
\begin{equation}
  \text{FWER} = \prob(V\geqslant1) \ .
  \label{eq:inference_fwer}
\end{equation}
This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$. Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$. This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
  \text{FWER} \leqslant \alpha \ .
\end{equation}
However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negatives. This is because the correction traded too many false positives for false negatives.

The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the PCER or FWER. The FDR is the proportion of false positives out of all positive results, that is
\begin{equation}
  \text{FDR} = \expectation\left[\dfrac{V}{R}\right]
  \ .
\end{equation}
It is defined that $V/R=0$ when $R=0$.

The BH procedure adjust the size of the test between the Bonferroni correction and the uncorrected test. It adapts to the data and choose different sizes for different data. The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(n)}$. Suppose a size $\alpha$ is provided beforehand. The size is then adjusted to
\begin{equation}
  \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
  \ .
\end{equation}
This test the statistics with $p$-values $p_{(1)},p_{(2)},\cdots,p_{(k)}$ as positive. For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes. For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.

The BH procedure comes from the fact that if all the statistics are null and independent, then the $p$-values are uniformly distributed \citep{simes1986improved}. However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}. It can be shown that the BH procedure controls the FDR such that
\begin{equation}
  \text{FDR}\leqslant\alpha
\end{equation}
\citep{benjamini1995controlling}.

In summary, the uncorrected, Bonferroni and BH correction controls for different error rates according to the threshold $\alpha$, summarised in Table \ref{table:inference_corrections}.

\begin{table}[htp]
    \centering
    \begin{tabular}{c|c}
        Correction&Controls for\\\hline
        No correction&$\text{PCER}\leqslant\alpha$\\
        Bonferroni&$\text{FWER}\leqslant\alpha$\\
        BH&$\text{FDR}\leqslant\alpha$
    \end{tabular}
    \caption{Different types of corrections for multiple hypothesis testing are listed here, along with what they control for.}
    \label{table:inference_corrections}
\end{table}

Consider a small example where a $200\times200$ section of the $z$ image was investigated, as shown Figure \ref{fig:inference_inferenceSubsample1_histogram}. The distribution of the test statistics looked Normal but not centred at zero, as a result using the BH procedure obtained a critical region of $|Z|>\input{../figures/inference/inferenceSubsample1_criticalBoundary.txt}$. Almost half of the pixels were tested positive. It is questionable whether such a number of positive results is sensible, in particular in an area where defects were not expected.

\begin{figure}[htp]
  \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_zImage.eps}
      \caption{Test statistics}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsample1_histogram.eps}
      \caption{Histogram of test in sub-image}
    \end{subfigure}
    }
    \caption{The resulting $z$ image is shown in a). A $200\times 200$ sub-image was taken shown by the dashed lines. A histogram of the test statistics in the sub-image is shown in b). The critical region was obtained by using the BH procedure at the 5\% FDR level.}
    \label{fig:inference_inferenceSubsample1_histogram}
\end{figure}

This problem commonly occur in large scale multiple hypothesis testing \citep{efron2004large} such as in microarrays \citep{hedenfalk2001gene, efron2002empirical, efron2003robbins}. It appears that the null distribution was misspecified as $Z_i|H_{0,i}\sim\normal(0,1)$ when in reality they are distributed as $Z_i|H_{0,i}\sim\normal(\mu_0,\sigma_0^2)$, where $\mu_0$ and $\sigma_0$ are the null mean and null standard deviation respectively.

In practice $\mu_0$ and $\sigma_0$ are unknown. The empirical null \citep{efron2004large} replaces the parameters of the null distribution with its estimate. Suppose $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ are the estimated null mean and null standard deviation respectively. The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\cdots,n$.

>>>>

\documentclass[twocolumn]{article}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements

\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{2}

\let\footruleskip\undefined
\usepackage{fancyhdr}
\pagestyle{plain}

\DeclareMathOperator{\variance}{\mathbb{V}ar}
\DeclareMathOperator{\normal}{N}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\addNumber}[1]{\protect\input{#1}\unskip}
\newcommand{\inputNumber}[1]{\protect\input{#1}\unskip}

\title{Local Normalisation using the Empirical Null for Inspection of Additive Manufacturing using X-Rays}
\date{2019}
\author{
  Sherman Lo \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams \and Jason Warnett
}

\begin{document}\sloppy

\maketitle

\begin{abstract}
X-ray computed tomography (CT) can be used for defect detection in additive manufacturing. The object is scanned at multiple angles to reconstruct the object in 3D space. The process can be time consuming. The aim is to investigate if it is possible to conduct defect detection from a single scan to speed up the quality control procedure. An experiment was conducted, a 3D printed sample was manufactured with voids to see if they can be detected.

Software, \texttt{aRTist}, was used to simulate the scan and it was compared with the x-ray acquisition under the face of uncertainty. Each pixel was treated as a hypothesis test. The software, and the information provided to it, was not perfect which led to model misspecification and incorrect inference. The empirical null filter was proposed. It locally normalise each test statistic using robust estimators of the mean and deviation. This reduces the number of false positives. Sensible inference was achieved in the simulation and experiment.
\end{abstract}

\section{Introduction}

Quality control in additive manufacturing (or 3D printing) can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared to the computer aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves calculations on acquisition of hundreds of angles of the sample.

Speeding up the quality control process on the production line could be done by doing inspection on a few number of x-ray images \citep{warnett2016towards}. These x-ray images are compared with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \texttt{aRTist} can simulate x-ray acquisitions of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the computer aided design (CAD) of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods.

A method was proposed to compare the x-ray image with \texttt{aRTist} by treating the simulation of \texttt{aRTist} as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. Beforehand however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of \texttt{aRTist} do not match up perfectly with the x-ray image, producing incorrect inference. The empirical null filter is demonstrated on simulated and real data.

\section{Method}

\subsection{Apparatus and Procedures}

A ABS plastic cuboid (\SI{4}{\centi\metre} $\times$ \SI{4}{\centi\metre} $\times$ \SI{6}{\centi\metre}) with voids was purposefully manufactured to see if they can be detected. The CAD shown in Figure \ref{fig:inference_testObject} was manufactured using a \emph{Fortus} 3D printer. The voids were of various diameters \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}. 6 voids for each diameter were designed in the CAD. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, otherwise they were arranged irregularly. The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$.

@@

The x-ray source used a tungsten filament with a copper filter. The current and voltage was set to \SI{250}{\micro\ampere} and \SI{80}{\kilo\volt} respectively. The exposure time was \SI{500}{\milli\second}. The x-ray detector is a \emph{Perkin Elmer XRD 1621 AN/CN} digital x-ray detector, producing a $2000\times 2000$ 16-bit image. Shading correction \citep{young2000shading, munzenmayer2003enhancing}, using a black image at \SI{0}{\kilo\volt} and a white image at \SI{80}{\kilo\volt}, were used to remove panel effects from the x-ray detector.

The 3D printed sample was scanned 20 times. The 20 x-ray images were spilt into 2. 19 random images were held out. The remaining image was used to compare with \texttt{aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.

\subsection{Statistical Methodology}

Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the scan and \texttt{aRTist}. A disagreement too big will classify that pixel as a positive result. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{scan}_{x,y} - \texttt{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan.

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated x-ray images of the 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed GLM \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable when working out the test statistics.

It was assumed that the grey values were Normal, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
\begin{equation}
Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{0,x,y}^2)
\end{equation}
for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively. Their estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ also respectively. Define the null hypotheses to be
\begin{equation}
  H_{0,x,y}:\mu_{x,y}=\widehat{\mu}_{0,x,y}
\end{equation}
which are tested against
\begin{equation}
  H_{1,x,y}:\mu_{x,y}\neq\widehat{\mu}_{0,x,y} \ .
\end{equation}
The empirical null filter aims to obtain the estimators $\widehat{\mu}
_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$. This is based on the empirical null \citep{efron2004large}.

To obtain the estimates, a circular kernel with radius $r$ was centred at $(x,y)$. All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{parzen1962on, friedman2001elements}
\begin{equation}
\widehat{p}_{Z_{x,y}}(z) = 
\frac{1}{nh}
  \sum_{i,j\in K_{x,y}}\phi\left(
    \dfrac{z_{i,j}-z}{h}
  \right)
\end{equation}
where $K_{x,y} = \text{kernel centred at }(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of pixels in $K_{x,y}$, similar to \cite{silverman1986density, sheather2004density}. The estimates were obtained by solving
\begin{equation}
\widehat\mu_{0,x,y} = \text{argmax} \widehat{p}_{Z_{x,y}}(z)
\end{equation}
using the Newton-Raphson method and
\begin{equation}
  \widehat{\sigma}_{0,x,y} = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z=\widehat{\mu}_{0,x,y}}
  \right]^{-1/2}
\end{equation}
\citep{efron2004large}. The test statistics were normalised using
\begin{equation}
  T_{x,y} = 
  \dfrac{
    Z_{x,y}-\widehat{\mu}_{0,x,y}
  }
  {
    \widehat{\sigma}_{0,x,y}
  } \ .
\end{equation}
All the normalised test statistics were converted to $p$-values
\begin{equation}
  p_{x,y} = 2(1-\Phi(|t_{x,y}|))
\end{equation}
and was used in the \cite{benjamini1995controlling} (BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.

\subsection{Software Development}

The empirical null filter was implemented using \texttt{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}.

\section{Simulation}

The empirical null filter was tested to see if it can detect simulated defects from a $256\times 256$ contaminated image. A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution. For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$. A $30\times 30$ square defect was simulated. A kernel can capture the entire defect if its radius is large enough.

Contamination is the result of a linear transform of the test statistics $Z_{x,y}$. For example. in this experiment, the image was multiplied by 2 and a gradient was added to it. Suppose the image does contain defects, then an example of a resulting distribution is
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
\end{align}
where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this experiment to simulate a contaminated image with defects. The contaminated square defected image is shown in Figure \ref{fig:inference_defectSquare2Example}.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
  \caption{A $256\times 256$ contaminated Gaussian image with a $30 \times 30$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

The contamination is a nuisance because the test statistics have larger variance and larger values at the two corners. This cause an inflation in false positives which leads to incorrect inference.

Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null. In this simulate example, it is about $r>54$. A kernel too small would treat the defects as null, making them difficult to detect.

The receiver operating characteristic (ROC) curve \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} was studied in this experiment. The ROC is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds. The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}. Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed thoroughly in \cite{cook2007use}.

An experiment was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$. Hypothesis testing was done on the uncontaminated and filtered contaminated image. The area under the ROC curve and various errors were recorded. This was repeated 100 times by simulating another contaminated image with a defect. To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination. The results are shown in Figure \ref{fig:inference_Experiment_DefectRadiusSquare}.

\begin{figure*}[p]
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $256 \times 256$ filtered contaminated Gaussian image with a $30\times 30$ square defect. Various kernel radiuses were investigated. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. The test was done at the 5\% FDR level. The box plot summarise the 100 repeats of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure*}

The results showed that the ROC area increased with kernel radius. This highlighted that a filtered image with a good radius kernel can performance almost as well as though there was no contamination. It also appeared that the optimal ROC area was achieved when using the kernel radius from the rule of thumb, making these results consistent with literature.

Preserving FDR is important because it keeps the FDR consistent before and after filtering. For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%. It appeared a large kernel radius helped preserve FDR control after filtering in these examples.

It appeared there is a kernel radius which minimised the type 2 error. A large kernel radius is required for FDR control but too large can lose statistical power.

\section{Results}

The empirical null was used on the real data. The x-ray image was manually segmented further as shown in Figure \ref{fig:inference_segmentFurther}. It was segmented using the edges of the projection of the 3D printed object. The empirical null filter was then used on each segment, or ROI, independently, ignoring any pixels outside the ROI the filter is working on. The resulting filtered segments were stitched together to form the resulting filtered image. The resulting inference is shown in Figure \ref{fig:inference_subroisep16120deg_inference_radius4}.

The larger defects were successfully highlighted by the hypothesis test. It can be seen that the empirical null mean did change face to face, resulting in a clear boundary set by the edges. This probably suggest that the contamination or inaccuracy from \texttt{aRTist} was face dependent.

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{../figures/inference/segment.JPG}
  \caption{The x-ray image was segmented further into 7 segments or ROI.}
  \label{fig:inference_segmentFurther}
\end{figure}

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$. a) X-ray image with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroisep16120deg_inference_radius4}
\end{figure*}
